stats-project

### 2020-12-05 R - Deliverable/MSDS 6371 - Project.Rmd
fix: as.factor on necessary categorical variables

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_train$Neighborhood = as.factor(data_train$Neighborhood )
data_test = as.data.frame(unclass(data_test))
data_test$Neighborhood = as.factor(data_test$Neighborhood )
# add new remodel variable
data_train$Remodel =ifelse(data_train$YearBuilt==data_train$YearRemodAdd, 0, 1)
data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
data_train$GrLivArea2 = data_train$GrLivArea^2
data_test$GrLivArea2 = data_test$GrLivArea^2
summary(data_train)
summary(data_test)

>>>>

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_train$Neighborhood = as.factor(data_train$Neighborhood)
data_train$HouseStyle = as.factor(data_train$HouseStyle)
data_train$KitchenQual = as.factor(data_train$KitchenQual)
data_train$SaleCondition = as.factor(data_train$SaleCondition)

data_test = as.data.frame(unclass(data_test))
data_test$Neighborhood = as.factor(data_test$Neighborhood )
data_test$HouseStyle = as.factor(data_test$HouseStyle)
data_test$KitchenQual = as.factor(data_test$KitchenQual)
data_test$SaleCondition = as.factor(data_test$SaleCondition)
# add new remodel variable
data_train$Remodel =ifelse(data_train$YearBuilt==data_train$YearRemodAdd, 0, 1)
data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
data_train$GrLivArea2 = data_train$GrLivArea^2
data_test$GrLivArea2 = data_test$GrLivArea^2
summary(data_train)
summary(data_test)
head(data_train)
